Vegetation regrowth/encroachment (gjengroing)

### 2023-10-19 gjengroing.Rmd

@@

```{r ref-open-enc, fig.cap="Refenerence vegetation height in wetland ecosystems under the forest line in Norway."}
refVaatmark %>%
  mutate(elevation = factor(elevation, levels = c("0-300", "300-600", "600-900", "900-1200", ">1200")),
         vegClimZoneLab = factor(vegClimZoneLab)) %>%
  ggplot(aes(x = elevation, y = ref))+
  geom_bar(stat="identity")+
  theme_bw(base_size = 12)+
  theme(axis.text.x = element_text(angle = -45, vjust = 0.5, hjust = 0.2, size = 12))+
  facet_wrap(.~vegClimZoneLab)+
  labs(y = "Reference vegetation height (m)",
       x = "Elevation (meters above sea level)")
```

>>>>

<!-- Limit code block height and force scrolling -->
```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

@@

```{r ref-wet-enc, fig.cap="Refenerence vegetation height in wetland ecosystems under the forest line in Norway."}
refVaatmark %>%
  mutate(elevation = factor(elevation, levels = c("0-300", "300-600", "600-900", "900-1200", ">1200")),
         vegClimZoneLab = factor(vegClimZoneLab)) %>%
  ggplot(aes(x = elevation, y = ref))+
  geom_bar(stat="identity")+
  theme_bw(base_size = 12)+
  theme(axis.text.x = element_text(angle = -45, vjust = 0.5, hjust = 0.2, size = 12))+
  facet_wrap(.~vegClimZoneLab)+
  labs(y = "Reference vegetation height (m)",
       x = "Elevation (meters above sea level)")
```
